---
title: "Simple prediction on Cats/Dogs"
author: "Kevin Wang"
date: "`r paste0('Initiated on 2020 Mar 7, compiled on ', format(Sys.time(), '%Y %b %d'))`"
output:
  html_document:
    code_folding: hide
    fig_height: 10
    fig_width: 10
    toc: yes
    number_sections: true
    toc_depth: 3
    toc_float: yes
editor_options: 
  chunk_output_type: console
---

# Summary

Acknowledgement: this document follow closely from https://adamspannbauer.github.io/2018/02/14/image-classification-r-and-python/. 

This is a simple R-Markdown file demonstrating the model that we will be utilising to make prediction (cat/dog) given a picture of the animal.

# Loading 

## Packages
```{r}
library(keras)
library(tidyverse)
```


## Model
```{r}
# load vgg19 model pretrained with imagenet
model = application_vgg19(weights = 'imagenet')
```


## Curated Cat/dog labels files

The pre-trained model only outputs breeds of the animal, not cats/dogs. The author made a curated list of cats/dogs on the [GitHub repo](https://github.com/AdamSpannbauer/keras_image_r_python/tree/master/data), but I consolidated these labels into one single CSV file in my [GitHub repo](https://github.com/kevinwang09/shiny_3888). 

```{r, eval = FALSE}
#function to read in files housing all cat/dog breeds in imagenet labels
read_dog_cat_labels = function(path) {
  labs = readLines(path)
  labs = trimws(unlist(strsplit(labs, ',')))
  labs = gsub('\\s+', '_', labs)
  return(labs)
}

dog_labs = read_dog_cat_labels('https://raw.githubusercontent.com/AdamSpannbauer/keras_image_r_python/master/data/dog_classes.txt')
cat_labs = read_dog_cat_labels('https://raw.githubusercontent.com/AdamSpannbauer/keras_image_r_python/master/data/cat_classes.txt')

labels_tbl = bind_rows(
  tibble(
    catdog = "cat",
    class_description = cat_labs
  ),
  tibble(
    catdog = "dog",
    class_description = dog_labs
  )
)

write_csv(labels_tbl, "supp/labels_tbl.csv")
```

```{r}
labels_tbl = read_csv("supp/labels_tbl.csv")
```


## Customised functions
```{r}
# define image preprocessor for use with keras vgg19
image_preprocessor = function(image_path) {
  image = image_load(image_path, target_size = c(224,224))
  image = image_to_array(image)
  image = array_reshape(image, c(1, dim(image)))
  image = imagenet_preprocess_input(image)
  return(image)
}

# Prediction based on image, with added labels
pred_cats_dogs = function(model, file_name){
  processed_image = image_preprocessor(file_name)
  
  imagenet_decode_predictions(predict(model, processed_image))[[1]] %>%
    left_join(labels_tbl, by = "class_description")
}
```

# Making prediction on a single picture

```{r}
download.file("https://s3.amazonaws.com/cdn-origin-etr.akc.org/wp-content/uploads/2017/11/12234558/Chinook-On-White-03.jpg", destfile = "tmp.jpg")

pred_cats_dogs(model = model, file_name = "tmp.jpg")
```


# Prediction on multiple images (Extension)
```{r}
# define image paths to classify
image_paths = list.files('images/', recursive = TRUE, full.names = TRUE)

# get model prediction
pred_list = purrr::map(
  .x = image_paths,
  .f = ~ pred_cats_dogs(model = model, file_name = .x))

pred_tbl = pred_list %>%
  bind_rows(.id = "image_paths")

pred_tbl %>%
  DT::datatable()
```


# Session info
```{r}
sessioninfo::session_info()
```